MSK I

### 2017-09-11 msk1.rmd
Updated yaml header to make it a4. Stuff american letter paper
sed -i 's/=>/$\rightarrow$/g' *
fixed typo

```
title: "MSK I"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output: pdf_document
```

@@

After primary survey => secondary survey

@@

> Found before 5am lying on floor, crying in pain, unable to get up. No PMHx of chest pain, palpitations, "fits, faints or funny turns" [pre-syncope/syncope?]. PMHx = {osteoarthritis, HTN, insomnia, hearing loss, BPH}. Meds = {atenolol [$\beta-1$ blocker; used for HTN], oxazepam [benzodiazepine; used for anxiety, insomnia, and alcohol withdrawal], panadol osteo [paracetamol; relief for osteoarthritis]}. Said he slipped on bath mat after waking up whilst going to the toilet. Falling $\rightarrow$ severe pain in left hip, felt unable to stand.

>>>>

---
title: "MSK I"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document
documentclass: article
classoption: a4paper
---

@@

After primary survey $\rightarrow$ secondary survey

@@

> Found before 5am lying on floor, crying in pain, unable to get up. No PMHx of chest pain, palpitations, "fits, faints or funny turns" [pre-syncope/syncope?]. PMHx = {osteoarthritis, HTN, insomnia, hearing loss, BPH}. Meds = {atenolol [$\beta_{1}$ blocker; used for HTN], oxazepam [benzodiazepine; used for anxiety, insomnia, and alcohol withdrawal], panadol osteo [paracetamol; relief for osteoarthritis]}. Said he slipped on bath mat after waking up whilst going to the toilet. Falling $\rightarrow$ severe pain in left hip, felt unable to stand.
